Triplet Extraction from sentences

### 2020-05-08 paper.tex
Final commit for Group 3

\author{Sumith Baddam, Deepthi Raghu, John Stein, ... \\
  Affiliation
  {\tt \{srbaddam, draghu, jodstein, ...\}@iu.edu} \\}

@@

\section{Previous Work}
Our research about the previous work for this task exposed us to two different approaches. Traditional triplet extraction and Open triplets extraction. In Traditional Extraction, the relations to be extracted are pre-defined. In Open Extraction, the relations are not pre-defined. The system is free to extract any relations it comes across while going through the text data. We also came across different methods from some of the research papers we read. Although many of these approaches involved building a neural model, we mainly focused on approaching the problem of triple extraction using a linguistic method (rule based extraction) because no labeled training data were available.

@@

\noindent \newline
One of the approaches for rule-based triple extraction was to perform dependency parsing by writing rules to identify compounds such as adjectives and modifiers from the dependency tree. The rules are specifically based on the 'tokenlist' and the 'dependency' parts of the JSON from the NLP-API.

\subsection{Method 1}
In this approach, the input is a list of files containing multiple sentences line by line. The output will be a list of JSONs corresponding to each sentence in the input files. \\
\noindent
For example, if the input is a file containing two sentences:

@@

    \textbf{method2\_relations\_graph\_draghu.json} and the line by line relation extraction (output2) is generated in \textbf{method2\_relations\_triples\_draghu.txt}
\end{itemize}
\newpage

@@

This is how we evaluated our work, presenting the evaluation scores in comparison to previous projects...

Describe manual evaluation methodology: (1) look at sentence, (2) observe extracted triplets, (3) observe annotations in context of how our rule-based approach is programmed.  Walk through several examples.

@@

One of the challenges encountered during the progression of various approaches to triple extraction relates to pre-suppositions about what the resulting relation set might contain, and how one might want to reason over those relations.  More specifically, the initial expectation among many in the class was that the relations extracted would always be of the form (subject, verb, object).  While it is true that this was the initial approach (easiest to accomplish), this expectation resulted in some implementation decisions on the part of group 3 and the API group which may constrain the versatility and power of the knowledge graph representation.  For example, as discussed in Section \ref{jodstein_experiments} above, the initial choice to extract verbs as the relation versus as an independent entity constrained the resulting knowledge graph in several ways:

>>>>

\author{Sumith Baddam, Deepthi Raghu, John Stein, Manisha Suresh Kumar, Rasmitha Choudary Koduru \\
  Affiliation
  {\tt \{srbaddam, draghu, jodstein, msureshk, rakoduru\}@iu.edu} \\}

@@

\section{Previous Work (srbaddam)}
Our research about the previous work for this task exposed us to two different approaches. Traditional triplet extraction and Open triplets extraction. In Traditional Extraction, the relations to be extracted are pre-defined. In Open Extraction, the relations are not pre-defined. The system is free to extract any relations it comes across while going through the text data. We also came across different methods from some of the research papers we read. Although many of these approaches involved building a neural model, we mainly focused on approaching the problem of triple extraction using a linguistic method (rule based extraction) because no labeled training data were available.

@@

\noindent
One of the approaches for rule-based triple extraction was to perform dependency parsing by writing rules to identify compounds such as adjectives and modifiers from the dependency tree. The rules are specifically based on the 'tokenlist' and the 'dependency' parts of the JSON from the NLP-API.

\subsection{Method 1}
In this approach, the input is a list of files containing multiple sentences line by line. The output will be a list of JSONs corresponding to each sentence in the input files. For example, if the input is a file containing two sentences:

@@

    \textbf{method2\_relations\_graph\_draghu.json} and the line by line relation extraction (output2) is generated in \textbf{method2\_relations\_triples\_draghu.txt}
\end{itemize}
\newpage
\section{Experiments (msureshk)}

Adding on to the previous experiment, this is Manisha Suresh's approach to extracting prepositional relation. Before we talk more about the implementations, the below are the 'carry forwards' from the previous experiment:
\begin{itemize}
    \item \textbf{The sequential parsing of token list:}

    The token list i indexed from 0 - (number of words in input text - 1) and we sequentially parse through each word to slot them into objects, subjects, verb or prepositions and also identify relations.

    \item \textbf{Sentences without subjects, have subject tagged as “<imperative-chef>":}

    Often, sentences may not have a subject. below is one such example from our food corpus:
    "Prepare the cake mixes according to the package directions."

    So, we use "<imperative-chef>" as a placeholder while also being relevant to the context.
    Extracted relation : \{'source': 'imperative-chef', 'relation': 'prepare', 'target': 'cake mix'\}

    \item \textbf{Sentences without objects, have object tagged as ’<None>’:}

    Similar to “<imperative-chef>", we use ’<None>’ to indicate the absence of an object.

    "Cook until cauliflower begins to soften, about 4 minutes."

    Extracted Relation : {'source': 'cauliflower', 'relation': 'cook', 'target': '<None>'}

    \item \textbf{Utilizing graph.py to give a graph object as the output:}

    \begin{itemize}
        \item Triples (Subject, Verb, Object)
        \item Event relation (Event2 occurs\_after Event1)
        \item Prepositional Relations (Event, preposition, object)
    \end{itemize}
     \item \textbf{Generation of Event ID:}

      Event ID is created by concatenating the ID of that node with its subject and object

      An Example of one such event would be: '1\_imperative-chef\_prepare\_cake mix'
\end{itemize}
This section has two parts to it, both of which are handled in \textbf{'relations\_msureshk.py'}:
\begin{itemize}
    \item To take care of some unrelated triplets that get generated as was mentioned in the previous experiment.
    \item To capture Prepositional Relations to add on to the triples.
\end{itemize}
Next, we shall discuss this in detail.
\subsection{Part 1 : Coherent Triple Extraction}
With the previous experiments, we successfully extracted all possible triples. Concretely, all the verbs, objects and subjects were captured and then a mechanism where from these three lists, all possible combinations and permutations of triples was implemented.
Though this would contain the correct triples, it would also contain some incoherent ones. Below is one such example:
\newpage
\textbf{Sentence : }

"Cook the fish 5 to 6 minutes and gently break up the haddock into chunks."\\

\textbf{Extracted Triples : }

\{'source': 'imperative-chef', 'relation': 'cook', 'target': 'fish'\}

\{'source': 'imperative-chef', 'relation': 'cook', 'target': 'haddock'\}

\{'source': 'imperative-chef', 'relation': 'break', 'target': 'fish'\}

\{'source': 'imperative-chef', 'relation': 'break', 'target': 'haddock'\}\\

To tackle this, we extract triples as we go instead of 'collecting' them for later. This helps with capturing prepositional relations as well. We assume that when prepositions or a punctuation is encountered, the subject-verb-object triple captured till then will be one triple. Then the verb is discarded to allow a new triple to form. So, working with the previous sentence, the new triples extracted are:\\

\textbf{\{'source': 'imperative-chef', 'relation': 'cook', 'target': 'fish'\}}

\textbf{\{'source': 'imperative-chef', 'relation': 'break', 'target': 'haddock'\}}\\

Although this did away with the extra triples, it also would miss out on triples in certain kinds of sentences. Recall that we discard verbs as and when a triple is extracted. To implement this, at a time, we can work with one verb only. So if a sentence has consecutive verbs, only the latest verb would be captured and any possible triples with the missed out verbs will also be missed out. Were we using the approach adopted in Deepthi's experiment, none of the triples would be missed out. To understand this better here's a comparison between the two approaches.\\

\textbf{Sentence:}\\

"Cover and cook until cauliflower begins to soften."\\

\textbf{Previous Extraction:}\\

\{'source': 'cauliflower', 'relation': 'cover', 'target': '<None>'\}

\{'source': 'cauliflower', 'relation': 'cook', 'target': '<None>'\}\\

\textbf{Current Extraction:}\\

\textbf{\{'source': 'cauliflower', 'relation': 'cook', 'target': '<None>'\}}\\

Note how the verb 'cover' wasn't captured as it was immediately succeeded without prepositions or punctuations by another verb. In short, this mechanism works well for parts of sentences with single verbs and for ones with more than one, only the triple with the latest verb will be captured.\\

\section{Part 2 : Prepositional Relations}

Keeping up with the same logic, we can now extract prepositional relations. Lets consider the following sentence:

\textbf{"Prepare the cake mixes according to the package directions."}

\begin{itemize}
    \item Here the preposition is "according to". Using our triple extraction mechanism, we first get the triple as such:

    \textbf{\{'source': 'imperative-chef', 'relation': 'prepare', 'target': 'cake mix'\}}

    \item This is now captured as an even as such: \textbf{'1\_imperative-chef\_prepare\_cake mix'}\\

Now, when we encounter our preposition ("according to"), we retain it separately and continue with our traversal to capture the compound object 'package directions'. When the next preposition or punctuation is encountered, we have a prepositional relation at hand from the previous iteration. For this example, the period encountered at the end is when we have our relation:\\

\textbf{\{'source': '1\_imperative-chef\_prepare\_cake mix', 'relation': 'according to', 'target': 'package direction'\}}\\

Together, the two relations extracted for the example sentence captures the essence of the sentence. Here are more examples capturing prepositional relations
\begin{itemize}
    \item Example 1

    \textbf{Sentence : }

    "Add panko and Parmesan to first bowl and mix with your hands."

    \textbf{Relations : }

    \{'source': 'imperative-chef', 'relation': 'add', 'target': 'panko'\}

    \{'source': 'imperative-chef', 'relation': 'add', 'target': 'Parmesan'\}

    \{'source': '30\_imperative-chef\_add\_Parmesan', \textbf{'relation': 'to'}, 'target': 'first bowl'\}

    \{'source': 'imperative-chef', 'relation': 'mix', 'target': 'first bowl'\}

    \{'source': '32\_imperative-chef\_mix\_first bowl', \textbf{'relation': 'with'}, 'target': 'hand'\}

    \item Example 2

    \textbf{Sentence:}

    "Arrange the pita quarters on a parchment-lined baking sheet."

     \textbf{Relations : }

     \{'source': 'imperative-chef', 'relation': 'arrange', 'target': 'pita quarter'\}

    \{'source': '15\_imperative-chef\_arrange\_pita quarter', \textbf{'relation': 'on'}, 'target': 'lined sheet'\}

\end{itemize}
\textbf{Running 'relations\_msureshk.py' :}\\

To run the code, execute relations\_msureshk.py and as arguments pass the file names in sequence. Example : \textbf{relations\_msureshk.py test1.txt test2.txt}\\

\textbf{relations\_graph\_msureshk.json} captures the graph object, R in JSON format and \textbf{relations\_triples\_msureshk.txt} contains the relations extracted for each line in the input file. Note that one of each o these two files will be generated for all input files (In this case, 'test1.txt' and 'test2.txt').

@@

This section describes the evaluation method followed for the work presented. Section 8.1 describes the evaluation method. Section 8.2 evaluates performance comparing to existing Open IE extractor. Section 8.3 compares few examples of triples in the existing and linguistic approaches. Section 8.4 describes the limitations of the evaluation.

\subsection{Evaluation Method}

We chose to calculate the precision, recall, F-measure and accuracy by manually comparing the machine annotations against the gold standard. We have arrived to a gold standard by manually extracting triples from the food corpus shared by the corpus team. We have considered ford corpus file having 100 lines of text for the ease of evaluation. (1)

Precision, Recall, F-measure and accuracy are traditional evaluation methods in information retrieval.~\cite{precision} 
For this task we defined precision as the fraction of returned extractions that are correct, and recall as the fraction of correct extractions in the total corpus. For each extracted triplet, we manually check whether it is correct or not. Following are the expressions used for Precision, Recall, F-measure and accuracy
    \begin{verbatim}
        precision: true positives (TP)/true positives (TP) + false positives (FP)
        recall : true positives(TP) /true positives (TP) + false negatives (FN)
        Accuracy = (TN + TP)/(TN+TP+FN+FP) 
        F1 = 2* precision*recall/precision+recall
    \end{verbatim}
\begin{enumerate}
    \item True Positive (TP) : A true positive test result is one that detects the right triple  when the triple is present in ground truth.
    \item True Negative (TN) : A true negative test result is one that does not detect the triple when the triple is not present in the ground truth.
    \item False Positive (FP) : A false positive test result is one that detects the triple when the triple is not present in ground truth.
    \item False Negative (FN) : A false negative test result is one that does not detect the triple when the triple is present in ground truth.
\end{enumerate}

We have also compared the triples extracted by Open IE with the gold standard and calculated the respective Accuracy, recall, precision score and compared both the results.

\subsection{Performance}

We started with analyzing the existing approaches to measure the performance. For neural approaches of extracting triples many follow supervised techniques to verify if the extracted triplet is positive or negative ~\cite{classification} but the most primarily taken approach is the ground-truth based approach. We have compared each triple manually with the ground truth to classify into positive and negative classes. Therefore we have restricted our evaluation to one approach and compare it with the existing approach. ~\cite{paul_groth,shi_yuan}

Stanford Open IE ~\cite{openIE_extractor} follows a linguistic approach to extract triples which is closer to the aim of the paper. So we chose to compare the results with Open IE. Open information extraction (open IE) refers to the extraction of relation tuples, typically binary relations, from plain text, such as (Mark Zuckerberg; founded; Facebook). The central difference from other information extraction is that the schema for these relations does not need to be specified in advance; typically the relation name is just the text linking two arguments.\newline

To extract triples from open IE we have used a python open IE module and run the script with the input file. We then compared the triples of open IE manually with the ground truth. Here are the respective scores obtained.
\newline

\includegraphics[width=9cm, height=2.5cm]{score.png}\newline

\noindent Due to the complexity and time constraints we have restricted the task of comparing every triple and classifying to positive and negative to one experiment. The code file to generate the open IE triples and data files for classification of triples are all uploaded on to github (1).

\subsection{Analysis}

When you compare the accuracy of both the approaches it is clear that the rule based approach followed in the paper yields better accuracy than Open IE since we have improved the rules like adding imperatives for the sentences where the subject is missing as discussed in the Experiments section.\newline

Here are some of the observations comparing manual extraction, open IE and the approaches discussed.
\begin{itemize}
\item Example 1
\begin{verbatim}
"When sauce is almost done, cook pasta in a large pot of boiling salted water, 
stirring occasionally, until al dente; drain pasta."

Manually Extracted: 
{'subject': 'chef', 'verb': 'cook', 'object': 'pasta'}
{'subject': chef, 'verb': 'stir', 'object': 'pasta'}
Open IE extracted: 
{'subject': 'sauce', 'relation': 'is', 'object': 'almost done'}
{'subject': 'sauce', 'relation': 'is', 'object': 'When done'}
{'subject': 'sauce', 'relation': 'is', 'object': 'When almost done'}
{'subject': 'cook pasta', 'relation': 'is in', 'object': 'large pot boiling'}
{'subject': 'sauce', 'relation': 'is', 'object': 'done'}
Extracted: 
{'sentence': 26, 'event': 27, 'subject': 'sauce', 'verb': 'be', 'object': 'cook'}
{'sentence': 26, 'event': 27, 'subject': 'sauce', 'verb': 'be', 'object': 'al'}
\end{verbatim}

Inference: Since the subject is already present our approach does not add an imperative subject but when you look at it manually adding imperative subject makes much more sense.

\subsection{Limitations}

The evaluation measures can be improved by constantly verifying the ground truth and also by implementing more set of rules and extending the discussed experiments. First challenge is to verify if the ground truth is accurate since the evaluation is on the basis of ground truth. Current approach to calculate precision and recall is based on true positives and negatives. Since these are also compared and calculated manually there might be an error rate in the final values.
\newline

\noindent There might be cases of correct triples not being detected manually but are generated by the code.
\begin{verbatim}
"Arrange in a single layer, then roast in upper third of oven until 
green beans begin to blister, about 15 minutes."

Manually Extracted: 
{'subject': 'chef', 'verb': 'arranges', 'object': 'green beans'}
{'subject': 'chef', 'verb': 'roasts', 'object': 'green beans'}
Open IE extracted: 
{'subject': 'upper third', 'relation': 'in roast is', 'object': 'about 15 minutes'}
{'subject': 'green beans', 'relation': 'begin to','object': 'blister'}
{'subject': 'sauce', 'relation': 'is', 'object': 'When almost done'}
{'subject': 'beans', 'relation': 'begin to', 'object': 'blister'}
{'subject': 'roast', 'relation': 'is in', 'object': 'upper third of oven'}
Extracted: 
{'sentence': 34, 'event': 33, 'subject': 'bean', 'verb': 'arrange', 'object': '<None>'}
\end{verbatim}

Inference : When you look at the above text {'subject': 'green beans', 'relation': 'begin to', 'object': 'blister'} is considered to be a valid relation which was overlooked manually and approach followed in Experiment 4 was unable to extract the right relation.
\newline

\noindent Example of a case where the JSON-NLP API fails to provide the right dependency parse tree.
\begin{verbatim}
"1 x 15 oz can cut wax beans."

Manually Extracted: {'subject': 'none', 'verb': 'none', 'object': 'can cut beans'}
Open IE extracted: {'subject': 'oz', 'relation': 'can cut', 'object': 'wax beans'}
Extracted: 
{'sentence': 12, 'event': 13, 'subject': 'oz', 'verb': 'cut', 'object': 'wax bean'}
\end{verbatim}

Inference : The API assumes that 'can cut' is a verb where as can cut beans is a single entity and can here refers to the container.

Also The evaluation of sequence of event is currently not considered there is a confusion for the approach followed for sequencing. The current approach is to add a counter to every sentence and increment it. This approach is agreed up on the basis if requirements of group 4 but we think that current approach does not make sense because event  sequence is formed on the basis of a recipe in this context.
\newline
For Example in the text sentence "Let all the ingredients sit and marinate for at least 30 minutes." depends on previous sequences where 'all the ingredients' are defined but according to the present approach we are providing a static counter number sequence to reduce the complexity of the task.
\newline
\newpage
\begin{itemize}
    \item Improvements and Further Evaluation :
    \begin{enumerate}
        \item Evaluate the results after integrating with the API team.
        \item Improve the correctness of the ground truth.
        \item Evaluation of triplets with event sequence.
        \item Extend the evaluation all the experiments discussed.
        \item Expand the ground truth data set to the entire food corpus.
    \end{enumerate}
\end{itemize}

\noindent (1) All the files and code can be viewed from\newline
https://github.com/dcavar/ML4NLP/commit/d0669d59e5096939c7a7c027ebc5b10d63539b29. 
Details about the files are mentioned in the README.md file.

@@

One of the challenges encountered during the progression of various approaches to triple extraction relates to pre-suppositions about what the resulting relation set might contain, and how one might want to reason over those relations.  More specifically, the initial expectation among many in the class was that the relations extracted would always be of the form (subject, verb, object).  While it is true that this was the initial approach (easiest to accomplish), this expectation resulted in some implementation decisions on the part of the Relation Extraction group and the API group which may constrain the versatility and power of the knowledge graph representation.  For example, as discussed in Section \ref{jodstein_experiments} above, the initial choice to extract verbs as the relation versus as an independent entity constrained the resulting knowledge graph in several ways:
